R Tools for Obspack, Receptors and Footprints (rtorf)

### 2024-08-20 README.Rmd
fix readme
site

---
title: "R Tools for Obspack, Footprints and Receptors (rtorf)"
output: github_document
---

@@

```{r sf, echo = TRUE, message=FALSE}
library(sf)
sdft <- st_as_sf(dft[stat == "mean"], 
                 coords = c("longitude", "latitude"), 
                 crs = 4326)
sdft$value <- sdft$value*1e09
plot(sdft["value"], 
     reset = FALSE, 
     axes = TRUE, 
     graticule = TRUE,
     pch = 16, 
     cex = 1.5, 
     pal = cptcity::lucky(colorRampPalette = T), #random
     main = NULL)
maps::map(add = T)
```

@@

```{r agg}
df4 <- obs_agg(dt = df3,
               cols = c("value",
                        "latitude",
                        "longitude",
                        "site_utc2lst"),
               verbose = T,
               byalt = TRUE)
```

>>>>

---
title: "R Tools for Obspack, Receptors and Footprints (rtorf)"
output: github_document
---

@@

```{r sfsave, echo = FALSE, message=FALSE}
library(sf)
sdft <- st_as_sf(dft[stat == "mean"], 
                 coords = c("longitude", "latitude"), 
                 crs = 4326)
sdft$value <- sdft$value*1e09
png("man/figures/plotsf.png", width = 2000, height = 1500, res = 200)
plot(sdft["value"], 
     reset = FALSE, 
     axes = TRUE, 
     graticule = TRUE,
     pch = 16, 
     cex = 1.5, 
     pal = cptcity::lucky(colorRampPalette = T), #random
     main = NULL)
maps::map(add = T)
dev.off()
```

```{r sf, echo = TRUE, message=FALSE, eval = FALSE}
library(sf)
sdft <- st_as_sf(dft[stat == "mean"], 
                 coords = c("longitude", "latitude"), 
                 crs = 4326)
sdft$value <- sdft$value*1e09
plot(sdft["value"], 
     reset = FALSE, 
     axes = TRUE, 
     graticule = TRUE,
     pch = 16, 
     cex = 1.5, 
     pal = cptcity::lucky(colorRampPalette = T), #random
     main = NULL)
maps::map(add = T)
```

![](man/figures/plotsf.png)

@@

```{r agg}
df4 <- obs_agg(dt = df3,
               cols = c("value",
                        "latitude",
                        "longitude"),
               verbose = T,
               byalt = TRUE)
```
